---
title: "Landa-ALDA assignment 2"
author: "Isidro Landa"
date: "September 13, 2017"
output: pdf_document
---

# Packages used
```{r}
library(lme4)
library(tidyverse)
library(haven)
library(sjPlot)
library(ggthemes)
library(broom)
library(merTools)

```

# Load data
```{r}
## Set working directory
setwd("C:/Users/Isidro/OneDrive/WUSTL/Coursework/F17/ALDA")

long <- read_sav("Landa-CC daily diary.sav")
```


# Basic regression
```{r}
regr.1 <- lm(er.avoid ~ day0, long)
summary(regr.1)
```


Probelms 1 - 4
# Intercept only model
  - Unconditional means model
```{r}

# Random (intercept) effect
mod.1 <- lmer(er.avoid ~ 1 + (1 | id), data = long)
summary(mod.1)

intercept_variance <- .4393
residual_variance <- .5450
icc <- intercept_variance/(intercept_variance + residual_variance)

icc

# Plotting random effects of intercept
sjp.lmer(mod.1, facet.grid = F, sort = "sort.all")
```
## There are mean differences in how much people avoid on day 1. ICC = .45 meaning that just under less than half of the variance is attributable to between person variation. 

# Extracting fitted information
```{r}
# head(ranef(mod.2))
# fixef(mod.2)
# aug_scores <- augment(mod.2, data = long)
```


# Adding time
  - Unconditional growth model
```{r}

mod.2f <- lmer(er.avoid ~ 1 + day0 + (1 | id), long)
summary(mod.2f)

mod.2 <- lmer(er.avoid ~ 1 + day0 + (1 + day0| id), long)
summary(mod.2)
sjp.lmer(mod.2, facet.grid = F, sort = "sort.all")
```
# On average, avoidance as an emotion regulation strategy doesn't significantly vary with time. However, when random effects are taking into account, the fixed effect is now significant with a standard deviation of 0.03, indicating individual differences around the average effect. 

# When we include a random effect of time in addition to a random effect of the intercept, the random and fixed effects of the intercept slightly increase. 

# Interpreting time: For every day, there is a quarter decrease in the likert rating for the outcome of avoidance, on average. However, there is a standard deviation of .03 (larger than the fixed effect).

Problem 6
# Create a density plot of random effects
```{r}
ggplot(x, aes(x = randeffects)) + 
  geom_histogram(binwidth = .2, colour = "black", 
                 fill = "sienna2", alpha = .5) + xlim(0, 1) +
                                              
#Include a density curve
  stat_function(fun = function(x, mean, sd, bw) {
    dnorm(x = x, mean = mean, sd = sd) * 10000 * bw },
          args = c(mean = mean(), sd = sd(x$Heads5), 
              bw = 0.2), color = "black", size = 1) +
  labs(list(title = "Binomial Distribution Simulation: Five Coin Flips", 
            x = "\nProportion of Heads", 
            y = "Count\n"))
```

Problem 7
#Create a catepilar plot of the random effects. Is there any person that seems odd in terms of a large standard errors around intercept and slope estimates?
```{r}
FEsim(mod.2)
re.sim <- REsim(mod.2)
```


Problem 8
# Create a plot of the trajectory, along with a spaghetti plot of each person’s individual slope. Set the alpha level (transparency) on the individual slopes to make them easier to see.

Problem 9
# Create a plot of the trajectory, along with a spagehtti plot of each person’s individual slope. Set the alpha level (transperancy) on the individual slopes to make them easier to see.


