---
title: "Landa-Intensive Longitudinal Data Analysis"
author: "Isidro Landa"
date: "September 28, 2017"
output: pdf_document
---

# Load packages
```{r}
rm(list=ls())

library(haven)
library(tidyverse)
library(magrittr)
library(ggplot2)
library(lme4)
library(psych)
library(reghelper)
```


# Load data
```{r, echo = FALSE}
## Set working directory
#setwd("C:/Users/Isidro/OneDrive/WUSTL/Coursework/F17/ALDA/Assignments/1-descriptives-and-graphs-isidrolanda")
setwd("Z:/Lab/Lab Members/Isidro/Assignments/")


erdata <- read_sav("Landa-CC daily diary.sav")
post <- read_sav("Campus Culture-Post malone.sav") 


erdata <- merge(erdata, post, all.x = T, by = "id") 
  # Merge time-invariant variables from post-survey
erdata %<>% arrange(id, day) 
erdata[is.na(erdata)] <- NA 
  # Imported data had NaNs, but only is.na worked, not is.nan
```


# Insert rows for missing time points (if needed)
## This makes it possible to test lagged effects
```{r}
# CC_new_rows <- tbl_df(expand.grid(unique(day$id), seq(1, 7, 1)) %>%
#             rename(id = Var1, day = Var2) %>%  
#               full_join(day))
#   # tbl_df (or can use 'as_tibble') creates a new data frame 
# 
# erdata <- arrange(CC_new_rows, id, day)
```


# Model 1: "New place" maladjustment moderators of the association 
# between rumination and homesickness: Academic or Social?

## Graphs
```{r}
# Raw fluctuation in homesickness
ggplot(erdata, aes(day, e.homesick, group = id)) + geom_line() + 
  geom_point() + facet_wrap(~id) + 
  xlab("Time (Days 1-7)") + ylab("Homesickness") + 
  ggtitle("Figure 1. Homesickness as a Function of Day") +
  theme_classic() +
  theme(legend.position = "none",
          axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), 
                                    hjust = .5))


# Spaghetti plot with average growth trajectory
erdata %>%
  ggplot(aes(x = day, y = e.homesick)) + 
    geom_smooth(aes(group = id), method = "lm", se = F, color = "gray", size = .2) +
    geom_smooth(method = "lm", se = F, color = "red", size = 1) +
    labs(x = "Day", y = "Homesickness", title = "Figure 2. Growth Curve") +
    ylim(1, 5) +
    theme_classic() +
    theme(legend.position = "none",
          axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .06))


# Different color for each participant

# erdata %>% 
#  ggplot(erdata, aes(day, er.rumin, group = id)) +
#   geom_point() + stat_smooth(method = "lm", se = F) +
#   aes(color = factor(id)) + guides(color = F) +
#     # Coloured by participant
#   theme_classic() + 
#   xlab("Day") + ylab("Emotion Regulation-Rumination") + ylim(1, 5) +
#   ggtitle("Rumination as a Function of Day")

```


# Creating new vars (moderators)
```{r}

# Create belonging uncertainty (BUN) and academic functioning (acad.fx) composites
erdata %<>% mutate(bun_m = bun1 + bun2 / 2, 
                   acadfx = acad.lost + acad.procrast + acad.uncertain +
                     acad.perform.r / 4)

# Belonging Uncertainty (bun)
  # bun1 - Sometimes I feel that I belong at Wash U, 
      # and sometimes I feel that I don't belong at Wash U
  # bun3 - When something bad happens, 
      # I feel that maybe I don't belong at Wash U

# Academic Functioning (acadfx)
  # acad.lost - How lost did you feel in your assignments?
  # acad.procrast - How much did you procrastinate on your assingments?
  # acad.uncertain - How uncertain did you feel of where your academic 
      # future/career was headed?
  # acad.perform - How satisfied were you with your academic performance?


# Correlations/internal consistency among items

# acad_df <- erdata %>% select(acad.procrast:acad.perform)
# keys = c(1, 1, 1, -1)
# psych::alpha(x = acad_df, keys = keys)
  # alpha = 0.68
# bun_df <- erdata %>% select(bun1, bun3)
# correlate(bun_df)
  # r = 0.69

erdata$suppress <- 6 - erdata$suppress
# Suppress
  # In general, how much did you try to keep your emotions to yourself during these
    #face-to-face interactions today?

erdata %<>% mutate(neg.m = (e.nerv + e.fear + e.hostile + e.guilty + e.shame + 
                     e.slug + e.sleepy) / 7)

```


# Rescaling
```{r}
# Make time interpretable making zero day 1
# erdata$day0 <- erdata$day - 1

# Person-centering (mostly)
# Calculate them within a seperate df
erdata_agg <- erdata %>% group_by(id) %>%
  summarize(er.rumin_agg = mean(er.rumin, na.rm = T),
            e.homesick_agg = mean(e.homesick, na.rm = T),
            suppress_agg = mean(suppress, na.rm = T)) 
  # Get aggregate/person- or group-centered scores; 
    #i.e., Mean for each person across their respective time points

erdata <- merge(erdata, erdata_agg, all.x = T, by = "id")
erdata %<>% mutate(er.rumin_pc = er.rumin - er.rumin_agg,
                   e.homesick_pc = e.homesick - e.homesick_agg,
                   suppress_pc = suppress - suppress_agg,
                   bun_gm = bun_m - mean(bun_m, na.rm = T),
                   acadfx_gm = acadfx - mean(acadfx, na.rm = T))
  # Subtract person's mean from their raw score to get person-centered 
  # For bun_gm we grand mean center because this is a time-invariant var

# all(erdata$er.rumin == erdata$er.rumin_pc + erdata$er.rumin_agg, na.rm = T) 
  # Check calculations; should get 'TRUE' if done correctly

```


# Modeling with a time-varying predictor
```{r}
# Unconditional means model (i.e., intercept and time only)
mod1a <- lmer(e.homesick ~ day0 + (1 | id), erdata)
summary(mod1a)
  # Intercept: Mean of homesickness when day = 0 (i.e., day 1)
  # Day: NS; but would be interpreted as an increase in homesickness each day

ICC(mod1a) # Plenty of within-person variance but slightly more bw-person

# Uncentered rumination predictor
mod1b <- lmer(e.homesick ~ day0 + er.rumin + (1 | id), erdata)
summary(mod1b)
  # Intercept: Mean of homesickness when day = 0, controlling for rumination levels
  # Rumination: For every 1-unit increase in rumination, there is the between effect 
    # 0.08 increase in homesickness 

# Add person-centered rumination instead
mod1c <- lmer(e.homesick ~ day0 + er.rumin_pc + (1 | id), erdata)
summary(mod1c)
  # Intercept: Similar; slightly larger when controlling for within rumination effect
  # Rumination: Similar; Now, the CONCURRENT association with homesickness due to 
  # person-centering
    # On days that rumination goes up, homesickness does too (not by much; 0.06)

```


# Examining predictions from week to week
## For example, does Rumination on day one predict Homesickness on day two,
## controlling for Homesickness on day one, and so forth.
```{r, echo = FALSE}
library(DataCombine) # To use 'slide()' function

# Here we will create a lagged variable for homesickness such that
# it's values will be shifted downward by one day.

# Create a time-lagged varaible for homesickness
erdata %<>% arrange(id, day)
erdata_lagg <- slide(erdata, Var = "e.homesick", GroupVar = "id", slideBy = -1)
  # Can slide by other values if theoretically meaningful

  ## Copy over NAs from original homesick into new lagged homesick var
  erdata_lagg %<>% mutate(next_home = ifelse(is.na(e.homesick), e.homesick,
                                             `e.homesick-1`))
  erdata$next_home <- as.numeric(erdata_lagg$next_home) 
    # Ensure they're sorted the same first & add to original dataset
  
  # Rationale: When data is shifted downward, 
  # actual values shift into cells (i.e., weeks) that were originally missing; 
  # we don't want to predict values for days they missed
  
 erdata %<>% select(next_home, everything()) # Move lagged var to the front
  
 

 # Create a time-lagged varaible for negative affect
erdata %<>% arrange(id, day)
erdata_lagg2 <- slide(erdata, Var = "neg.m", GroupVar = "id", slideBy = -1)

  ## Copy over NAs from original homesick into new lagged homesick var
  erdata_lagg2 %<>% mutate(next_neg = ifelse(is.na(neg.m), neg.m,
                                             `neg.m-1`))
  erdata$next_neg <- as.numeric(erdata_lagg2$next_neg) 
    # Ensure they're sorted the same first & add to original dataset
  
  # Rationale: When data is shifted downward, 
  # actual values shift into cells (i.e., weeks) that were originally missing; 
  # we don't want to predict values for days they missed
  
 erdata %<>% select(next_neg, neg.m, everything()) # Move lagged var to the front
  
```


# Model 1b - Time-lagged models with time-invariant predictors
```{r}
# Does rumination predict homesickness controlling for previous day homesickness?
mod2a <- lmer(next_home ~ day0 + e.homesick_pc + er.rumin_pc + (1 | id), erdata)
summary(mod2a)
  # No
  # Homesickness: has sizable variation around random effect
  # Rumination: has sizable variation around random effect

# Does this change with the introduction of a time-invariant predictor?
mod2b <- lmer(next_home ~ day0 + e.homesick_pc + er.rumin_pc*bun_gm +
                (1 | id), erdata)
summary(mod2b)
  # No cross-level interaction 

mod2c <- lmer(next_home ~ day0 + e.homesick_pc + er.rumin_pc*acadfx_gm +
                (1 + e.homesick_pc + er.rumin_pc | id), erdata)
summary(mod2c)
  # No cross-level interaction 

# Can informally check autocorrelation for homesickness by correlating orginal and lagged var
mod2 <- lmer(next_home ~ e.homesick + (1 | id), erdata)
summary(mod2)
```


# Does homesickness predict anxiety? Is this stronger for those high in suppression?
```{r}


mod3 <- lmer(neg.m ~ day0 + e.homesick_pc + (1 + day0 + e.homesick_pc | id), erdata)
summary(mod3)
  # Day: Negative affect decreases by -0.04 each day
  # Homesickness: On days that homesickness increases, negative affect does too
    # By 0.14, t = 5.36
  # There is decent amount of variation around random effects, but fixed dont change

mod3b <- lmer(neg.m ~ day0 + e.homesick_pc + suppress_pc + (1 | id), erdata)
summary(mod3b)
  # Suppress: Counterintuitively, negative affect actually decreases on days that
    # suppression increases (-0.12, t = -5.09)

mod3c <- lmer(next_neg ~ day0 + e.homesick_pc*suppress_pc + (1 | id), erdata)
summary(mod3c)
  # Main effects or interactions no longer significant; model saturated? Small N?
 
```



